---
title: "*Project title*"
subtitle: "Project Plan"
author: "Prepared by: "
output:
    word_document: default
    pdf_document: default
knit: (function(inputFile, encoding){
    rmarkdown::render(inputFile, encoding=encoding, output_format = 'all')})

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(dplyr)
```

|                        |                     |
|-----------------------:|:--------------------|
| Period of Performance: |                     |
| Level of Effort:       | *estimated # hours* |

## Executive summary
*1 - 3 paragraph overview of the project plan*


## Goals and Objectives
*Description of the project scope and project goals. Be sure to include both what will be done and will not be done.*
    
* *Bulleted list of deliverables*


## Methods
*High level plan of execution, including methods, project phases, etc...*


## Resources
*Existing resources, cost (FTE and other expenses), roles and responsibilities of required analysts.*


## Communications plan
There will be two tiers of communications for this project:

* Regular: Regular communications will consist meetings and presentations, as well as electronic communications such as email, figures, tables and manuscripts. All electronic communications will be logged in the Analysis Management Portal ([AMP](https://abcs-amp.cancer.gov/)) to maintain transparency.
* Monthly report: Project summary updates will be shared in the monthly report and will include:
    * Project status
    * High-level scientific/technical update (1 - 2 sentences)
    * Current issues (e.g. changing scope, changes to level of effort, anything that may lead to project failure)
    * Other project metrics (i.e. period of performance, percent complete, actual vs planned level of effort)


## Stakeholders

```{r table}
tibble(Affiliation = c('stakeholder affiliation'),
       Stakeholder = c('list all stakeholders'),
       Email = c('email'),
       `Communication` = c('communication tier')) %>%
    kable()
```


## Risks and Opportunities

* Risks
    * *Bulleted list of risks with a brief description of risk mitigation*
* Opportunities
    * *Bulleted list of opportunities with a brief description of opportunity enhancement*


*electronic signatures may be included at the bottom of this document*
