---
title: "Project management principles and policies"
output: 
    word_document: default
    md_document: default
knit: (function(inputFile, encoding){
    rmarkdown::render(inputFile, encoding=encoding, output_format = 'all')})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(dplyr)
```

The project management principles and policies outlined in this document are intended to maintain transparency in our relationships with the government while minimizing administrative overhead. As such, we have taken a simplified approach to project management with three phases. More complex projects will require additional project management steps in each phase.

* Project Approval
    * Project initiation
    * Project plan (more detailed plans required for more complex projects)
    * Project approval
* Project Execution
    * Carry out project tasks according to the principles and policies outlined in the document titled Reproducible Research.
    * Project monitoring (requirements vary by level of complexity)
* Project Closeout
    * Publication
    * Project archival


## Project Approval

After project initiation and completion of the project plan, all project documents will be routed to the appropriate individuals listed in the table below for notification and/or approval using the communications tab in [AMP](https://abcs-amp.cancer.gov). ABCS and government approvals must be documented in AMP prior to project execution.

```{r Table1}
tibble(Level = c('< 80 hrs', '< 200 hrs', '≥ 200 hrs'),
       `Team Lead` = rep('Approve', 3),
       `ABCS Rep` = c('Notify', rep('Approve', 2)),
       `Govt Rep(s)` = c(rep('Notify', 2), 'Approve')) %>%
    
    kable()
```

### Project Initiation
Projects are officially initiated when a request is submitted via the [ABCS project request form](https://ncifrederick.cancer.gov/bids/abcs/project-request/). Information required includes but is not limited to the PI requesting the project and a description of the work to be completed.

Once a project request is completed an ABCS representative will triage the request and assign a lead analyst and other analysts as needed. The lead analyst is then responsible for providing the following additional information prior to project approval:

* Estimated level of effort (LOE) category:
    * < 80 hours
    * < 200 hours
    * ≥ 200 hours
* GitHub repository link
* Methods summary (not required for projects requiring <80 hours)
* Project plan (not required for projects requiring <200 hours)

### Project Planning
For simple projects requiring less than 80 hours of effort, the project scope and aims outlined in the description should correlate with the stated level of effort. Additional follow up and justification may be required prior to approval.

#### Methods Summary
Projects with an estimated LOE greater than 80 hours require a one to two paragraph description of the planed methods to be used for the project prior to approval. This will be included in the project metadata in AMP and should include the following information:

* Proposed methods to meet project aims described in the project description.
* Analysts expected to contribute to the project.

#### Project Plan
Projects with an estimated LOE greater than 200 hours (approximately 0.1 FTEs over the course of a year) require a signed project plan prior to commencement of work. This should follow the standard template and be uploaded to [AMP](https://abcs-amp.cancer.gov) for consideration and approval (links for the template in: [Rmarkdown]() and [Word]()).


## Project Execution
Once all requisite approvals have been granted, work on the project may begin. The project should employ reproducible research best practices as outlined [here](). This includes but is not limited to the following:

* Code is versioned and regular commits are pushed to GitHub.
* Communications are logged in [AMP](https://abcs-amp.cancer.gov/).
* All other research objects are stored in [AMP](https://abcs-amp.cancer.gov/), with the exception of large data sets.

Changes in scope should be brought to the attention of an ABCS representative and documented in [AMP](https://abcs-amp.cancer.gov/).

### Project Monitoring
The following project metrics and metadata should be kept up to date in [AMP](https://abcs-amp.cancer.gov/):

* Project status
* Project notes (1-2 sentence, scientific/technical update)
* Current issues (e.g. changes in scope, changes in estimated level of effort, risks that are threatening the project)
* Approximate hours spent on the project (*working with Tyler on hours tracking*)
* Approximate percent complete (one of four categories):
    * < 25%
    * 25 - 75%
    * 75 - 95%
    * > 95%

Differences between planned LOE and actual LOE should be noted as soon as possible to allow time to secure any additional approvals necessary without impacting the project. Once the actual LOE has exceeded the planned LOE, work should stop until the requisite approvals have been granted.

Monthly reports will be run on the evening of the 10th day of each month and shared with government Contracting Officer Representatives (CORs) and subject matter experts as designated by each COR.


## Project Closeout
When projects are completed or canceled, the following actions should be taken:

* Project data should be archived (additional details needed).
* GitHub repository actions:
    * Ensure any DOIs, publication references, and/or links to archived data are included in the README.
    * Ensure the public/private status of the repository is correct.
    * Analysis repositories and unsupported software repositories should be archived (see GitHub repository settings > Options > Danger Zone).
* Submit a [new project request](https://ncifrederick.cancer.gov/bids/abcs/project-request/) for all completed software projects that will require ongoing maintenance and support. The level of effort for maintenance should reflect the expected number of hours required for maintenance each year.
* Project metadata should be reviewed and updated appropriately in [AMP](https://abcs-amp.cancer.gov/).
